A Horrocks-type theorem for even orthogonal $K_2$

### 2020-04-07 dl-paper.tex
Minor fixes

\begin{rem} \label{rem:recognition}
  From the above definition it follows that an element $z_\gamma(Xf, \xi)$ is a generator of type 1 provided $\gamma\neq\pm\alpha$ and $\gamma \not \perp \alpha$. Since $x_\gamma(Xf) = z_\gamma(Xf, 0)$, it follows that $x_{\gamma}(Xf)$ is also a generator of type 1. In particular, if $\beta, \alpha + \beta \in \Phi$ then $x_{\pm(\alpha+\beta)}(Xf)$ is a generator of type 1 and $x_{\alpha+\beta}(f)$ is a generator of type 2.
\end{rem}

@@

\begin{rem} \label{Pstar-char} 
By the above lemma and~\cref{rem:DS} the subgroup $\widetilde{P}_{\alpha, M}(*)$ coincides with the preimage of the subgroup $Z_\alpha(A, M) \leq \overline{\St}(\Phi, A, M)$ under the homomorphism \[ev_{X=0}^*\colon \overline{\St}(\Phi, A[X], M[X]) \to \overline{\St}(\Phi, A, M).\] \end{rem}

@@

In the sequel we often use the following property of $S_\alpha(a, -)$.
\begin{lemma} \label{lem:Smult}
For $g_1 \in P_\alpha(m)$, $g_2 \in P_\alpha(*)$ one has
$S_\alpha(a, g_1\cdot g_2) = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right).$
\end{lemma} \begin{proof} Assume $g_2\in P_\alpha(m')$ for some $m' \in M$, so that $g_1 \cdot g_2 \in P_\alpha(m + m')$. The assertion now follows from the definition of $S_\alpha(a, -)$ and~\eqref{eq:symbol-properties}:
\begin{multline*} S_\alpha(a, g_1 \cdot g_2) = x_\alpha(aX^{-1}) \cdot g_1 \cdot g_2 \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1+am+am'}\right) \cdot \{X, 1 + am + am'\} = \\ = x_\alpha(aX^{-1}) g_1  x_\alpha\left(-\tfrac{aX^{-1}}{1+am}\right) \cdot x_\alpha\left(\tfrac{aX^{-1}}{1+am}\right) g_2 x_\alpha\left(-\frac{\tfrac{a}{1+am}\cdot X^{-1}}{1 + \tfrac{a}{1+am}\cdot m'}\right) \cdot \{X, (1+am)\left(1 + \tfrac{am'}{1+am}\right)\} = \\ = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right). \qedhere \end{multline*}
\end{proof}
It is clear that the restriction of the map $S_\alpha(a, g)$ to the subgroup $P_\alpha(0)$ coincides with the homomorphism of left conjugation by $x_\alpha(aX^{-1})$.
\begin{lemma}\label{P0_conj} The subgroup $P_\alpha(0)$ is stable under conjugation by $x_\alpha(aX^{-1})$ for arbitrary $a\in A$. \end{lemma}
\begin{proof} ??? \end{proof}

@@

\begin{corollary} \label{K-a-b-cor2}
 One has $\widetilde{P}_\alpha(0) \cap K(A[X], M[X]) =  \widetilde{K}(\alpha, \beta) \cdot X_{-\beta}(M \cdot X).$ 
\end{corollary}
\begin{proof} ??? \end{proof}

@@

\begin{lemma} \label{P0_conj-alternative} The subgroup $P_\alpha(0)$ is stable under conjugation by $x_\alpha(aX^{-1})$ for arbitrary $a \in A$. \end{lemma}
\begin{proof} Since any subgroup $H \leq \St(\Phi, A[X], M[X])$ satisfies $H = \left(H \cap K(A[X], M[X])\right) \rtimes ev^*_{X=0}\left(H\right)$, we obtain from~\cref{rem:DS} that
$\widetilde{P}_\alpha(0) =  \left(\widetilde{K}(\alpha, \beta) \cdot X_{-\beta}(M \cdot X)\right) \rtimes Z_\alpha(A, M).$

@@

>>>>

\begin{rem} \label{rem:recognition}
  From the above definition it follows that an element $z_\gamma(Xf, \xi)$ is a generator of type 1 provided $\gamma\neq\pm\alpha$ and $\gamma \not \perp \alpha$. Since $x_\gamma(Xf) = z_\gamma(Xf, 0)$, it follows that $x_{\gamma}(Xf)$ is also a generator of type 1. In particular, if $\beta$ is such that $\alpha + \beta \in \Phi$ then $x_{\pm(\alpha+\beta)}(Xf)$ is a generator of type 1 and $x_{\alpha+\beta}(f)$ is a generator of type 2.
\end{rem}

@@

\begin{rem} \label{Pstar-char} From the above lemma and~\cref{rem:DS} it follows that the subgroup $\widetilde{P}_{\alpha, M}(*)$ admits decomposition $\widetilde{P}_{\alpha, M}(*) = Z_\alpha(A, M) \ltimes K(A[X], M[X]).$ \end{rem}

@@

In the sequel we often use the following property of $S_\alpha(a, -)$.
\begin{lemma} \label{lem:Smult}
For $g_1 \in P_\alpha(m)$, $g_2 \in P_\alpha(*)$ one has
$S_\alpha(a, g_1\cdot g_2) = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right).$
\end{lemma} \begin{proof} Assume $g_2\in P_\alpha(m')$ for some $m' \in M$, so that $g_1 \cdot g_2 \in P_\alpha(m + m')$. The assertion now follows from the definition of $S_\alpha(a, -)$ and~\eqref{eq:symbol-properties}:
\begin{multline*} S_\alpha(a, g_1 \cdot g_2) = x_\alpha(aX^{-1}) \cdot g_1 \cdot g_2 \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1+am+am'}\right) \cdot \{X, 1 + am + am'\} = \\ = x_\alpha(aX^{-1}) g_1  x_\alpha\left(-\tfrac{aX^{-1}}{1+am}\right) \cdot x_\alpha\left(\tfrac{aX^{-1}}{1+am}\right) g_2 x_\alpha\left(-\frac{\tfrac{a}{1+am}\cdot X^{-1}}{1 + \tfrac{a}{1+am}\cdot m'}\right) \cdot \{X, (1+am)\left(1 + \tfrac{am'}{1+am}\right)\} = \\ = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right). \qedhere \end{multline*}
\end{proof}
It is clear that the restriction of the map $S_\alpha(a, g)$ to the subgroup $P_\alpha(0)$ coincides with the homomorphism of left conjugation by $x_\alpha(aX^{-1})$.

@@

\begin{corollary} \label{K-a-b-cor2}
 One has $\widetilde{P}_{\alpha, M}(0) \cap K(A[X], M[X]) =  \widetilde{K}(\alpha, \beta) \cdot X_{-\beta}(M \cdot X).$ 
\end{corollary}
\begin{proof} ??? \end{proof}

@@

\begin{lemma} \label{P0_conj} The subgroup $P_\alpha(0)$ is stable under conjugation by $x_\alpha(aX^{-1})$ for arbitrary $a \in A$. \end{lemma}
\begin{proof} Since any subgroup $H \leq \St(\Phi, A[X], M[X])$ satisfies $H = \left(H \cap K(A[X], M[X])\right) \rtimes ev^*_{X=0}\left(H\right)$, we obtain from~\cref{rem:DS} that
$\widetilde{P}_\alpha(0) =  \left(\widetilde{K}(\alpha, \beta) \cdot X_{-\beta}(M \cdot X)\right) \rtimes Z_\alpha(A, M).$

@@

\subsection{The map \texorpdfstring{$S_\alpha$}{Sa} and its properties.}
